Initial Analysis

### 2019-05-28 Initial_Analysis.Rmd
Model Results code

```{r, Trans_Results, eval = F, echo = F}

# Result 1. Number of tran spp per EEZ

Spp_Trans %>% 
  group_by(Name,TaxonKey) %>% 
  summarise(Mean_Index = mean(Trans_Index)) %>%  # The higher the less uncertain
  mutate(Uncert = ifelse(Mean_Index >= 0.50 ,"50 %",
                         ifelse(Mean_Index >= 0.25 ,"25 %",
                                ifelse(Mean_Index >= 0.10,">10 %","No Trans")))
         ) %>% 
  group_by(Name,Uncert) %>%
    summarise(nspp=n()) %>%
  ggplot(.,
         aes(
           x = Name,
           y = nspp#,
           # fill = Model
         )
         )+
  geom_bar(stat ="identity") +
  facet_wrap(~Uncert)

# Result 2. List of Countries that share the Species ####

Spp_Trans %>% 
  group_by(Name,TaxonKey,Neighbor_Territory) %>% 
  summarise(Mean_Index = mean(Trans_Index)) %>%  # The higher the less uncertain
  mutate(Uncert = ifelse(Mean_Index >= 0.10 & Mean_Index <= 0.25,"10 %",
                         ifelse(Mean_Index >= 0.25 & Mean_Index <= 0.50,"25 %",
                                ifelse(Mean_Index >= 0.50,">50 %","No Trans")))
         ) %>% 
    group_by(Name,Neighbor_Territory,Uncert) %>% 
    summarise(nspp=n())

@@

```{r World_Trans_Spp, eval = F,echo = T,warning = F,message = F}

World_Trans_Spp <- function(Species_List,Data_Path,Result){

  # Repeat for each species
  for (s in 1:nrow(Species_List)){ # Original code

    # Load species distribution data
    Species_Distribution_Path <- paste(Data_Path,Species_List[s,2],".csv",sep="")

    # Reads file
    Species_Distribution_Data <- read.csv(Species_Distribution_Path)

    # Pastes species name
    Species_Name = Species_List[s,1]

    # Call function to determine transboundary species
    Partial <- Trans_Spp_Fun(Species_Distribution_Data,
                             DBEM_Neighbors_Data,
                             Neighbors) %>% 
      mutate(Species = ifelse(Trans > 0,paste(Species_Name),NA)) # Include species name

    ### Result 1. Numnber of transboundary species by Country ####
    if(s == 1){
      Trans_Country = Partial
    }else{
      Trans_Country[,3] <- Trans_Country[,3] + Partial [,3] # Sum transboundary species
      Trans_Country[,4] <- Trans_Country[,4] + Partial [,4] # Sum Indexes within eez with TS
      Trans_Country[,5] <- ifelse(Trans_Country[,4] >= 0, paste(Trans_Country[,5],Partial[,5], sep=";"),Trans_Country[,5]) # Paste the species that are transboundary
    }

    # Result 2. Number of Countries per Transboundary Species ####

    Countries_with_Specie <- Partial %>% 
      filter(Trans == 1) %>% 
      group_by(Neighbor_Territory) %>% 
      summarise() %>% 
      summarise(Number_EEZ = n(),
                Countries = paste(Neighbor_Territory,
                                  collapse = ";")
      ) %>% # Number of territories in this species
      mutate(Species = Species_Name)

    if(s == 1){
      All_Countries_with_Specie <- Countries_with_Specie
    }else{
      All_Countries_with_Specie <- All_Countries_with_Specie %>% 
        bind_rows(Countries_with_Specie)
    }

  }# Closes species list

  # Function return
  if(Result =="Country"){ # returns results based on countries 
    return(Trans_Country)
  }
  if(Result == "Species"){ # returns results based on species 
    return(All_Countries_with_Specie)
  }
}

### Testing Function ####
# (Works!!!!!!!!)

### Dummy data ###
# SppA <- Julianus_Coor %>% 
#   filter(V1 >= 100000)
# 
# SppB <- Julianus_Coor %>% 
#   filter(V1 <= 100000)

# write.csv(SppB,
#           "456.csv",
#           row.names = F)

Dummy_Species <- data.frame(
  Species = c("SpeciesA","SpeciesB"),
  TaxonKey = c(123,456)
  )

D_Path <- "./Data/"

Function_Test <- World_Trans_Spp(Dummy_Species,D_Path, Result = "Country")

@@

```{r Final_Analysis, eval = F, echo=F}

# Varibales needed
# Species_List
# Data_Path

# Data_Path <- Drobo... Gabs... Distributions...
# DBEM_Species <- Selected_Species

# World_Trans_Spp(DBEM_Species,Data_Path)

>>>>

```{r Fun_GetTransResults, eval = T}

GetTransResults=function(Spp){

  # Set the path for each file
  Distpath <- paste(Results_Path,Spp,sep="")

  # Loads all files in a df
  Load_Data <- bind_rows(lapply(Distpath, FUN=fread))

  return(Load_Data)

@@

## Number of transboundary species per country

```{r Load_Data, eval = T}

# Transboundary data
Spp <- list.files(Results_Path)
Results_Data <- GetTransResults(Spp)

# TI of 10% and MI > 50

TenFifty <- Results_Data %>% 
  filter(Model_Index >= 50,
         Trans_Index >= 0.10) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(n_Trans_Spp = n()) %>% 
  filter(Model_Index == 50)
  head(Results_Data)

# SAU shapefile

World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

head(World_EEZs)

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 3832) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% 
  left_join(TenFifty, by ="Name") %>% 
  filter(!is.na(n_Trans_Spp)) %>% 
  st_transform(crs = 4326)

head(World_EEZs_simple)

ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_Trans_Spp))

@@

```{r, Trans_Results, eval = F, echo = F}
```
